%!TEX encoding = UTF8
%!TEX root =cv-llt.tex

\begin{rubric}{Internship Experience}
	\entry*[Oct 2024 -- Aug 2025]%
	\textbf{Software Development \& Product Application Intern,} Shanghai LEDA Software Technology
	\par \textbf{Responsibilities:} Participated in the localization substitution and optimization of EDA tools in multiple partitions (e.g., XPU, GPU) on SMIC process nodes.
	Responsible for building the workflow and optimizing PPA results for the Pre-CTS stage using domestic EDA tools.

	\entry*[Oct 2023 -- Sep 2024]%
	\textbf{Software Development Intern,} Shanghai LEDA Software Technology
	\par \textbf{Responsibilities:} Developed a timing prediction tool using placement results to bridge logic synthesis and physical design.
	This allowed for re-synthesis flow, which optimized the netlist and placement for better performance.

	\entry*[Jul 2021 -- Sep 2023]%
	\textbf{Software Development Intern,} Shanghai LEDA Software Technology
	\par \textbf{Responsibilities:} Optimized wirelength and prevented timing violations using analytical placement methods.
	Developed and integrated custom algorithms into domestic EDA tools, achieving superior PPA results on industrial benchmarks.
	\par \textbf{Publications:} \emph{Electrostatics-based analytical global placement for timing optimization} \cite{lin2024electrostatics}; \emph{An Analytical Placement Algorithm with Routing topology Optimization} \cite{wei2024analytical}

	\entry*[Sep 2020 -- Jun 2021]%
	\textbf{Software Development Intern,} Shanghai Fudan Microelectronics Group
	\par \textbf{Responsibilities:} Contributed to the development of EDA tools for FPGA design.
	Assisted in developing a detailed placement tool for FPGAs, where the related algorithms effectively improved the timing quality of FPGA layouts.

\end{rubric}
